NEED TITLE

### 2014-12-09 ms.tex
Updated captions for fig:snapshots and snapshots2

\begin{figure*}
\plottwo{movie_disk_0132_0001.png}{movie_disk_0132_0003.png}
\plottwo{movie_disk_0132_0000.png}{Disk_0132_0000.png}
\caption{{\bf Change plots to show a zoom out for 132 and zoom in on the three regions that are the same} Slices along the angular momentum axis of four zoomed in simulation. To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector. We then take a slice in the plane normal to the angular momentum to plot the regions around these dense points. \label{fig:snapshots}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.48\textwidth]{movie_disk_0132_0002.png}
\includegraphics[width=0.48\textwidth]{movie_disk_0132_0004.png}
\centering{\includegraphics[width=0.48\textwidth]{Disk_0132_0002.png}}
\caption{{\bf Do same for other plots in 132} Slices along the angular momentum axis of four zoomed in simulation. To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector. We then take a slice in the plane normal to the angular momentum to plot the regions around these dense points. \label{fig:snapshots 2}}
\end{figure*}

>>>>

\begin{figure*}
\plottwo{movie_disk_0132_0001.png}{movie_disk_0132_0003.png}
\plottwo{movie_disk_0132_0000.png}{Disk_0132_0000.png}
\caption{The upper frames, and the bottom left frame show slices along the angular momentum axis of three local particles in one of the regions demonstrating significant star formation.  Each of the zoomed-in slices have a radius of $0.02$ pc.  To determine the angular momentum axis, we take a $0.01$ pc region about the densest local point and calculate the angular momentum vector.  We then take a slice in the plane normal to the angular momentum vector to plot the regions around these dense points.  The bottom right frame shows the zoomed-out region of formation, with a radius of $1.5$ pc.    \label{fig:snapshots}}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.48\textwidth]{movie_disk_0132_0002.png}
\includegraphics[width=0.48\textwidth]{movie_disk_0132_0004.png}
\centering{\includegraphics[width=0.48\textwidth]{Disk_0132_0002.png}}
\caption{The upper frames show the zoomed-in slices along the angular momentum axis of the local particles in the second region of significant star production.  Again, each of the zoomed-in slices have a radius of $0.02$ pc.  The bottom frame shows the zoomed out region, with a radius of $1.5$ pc.  \label{fig:snapshots 2}}
\end{figure*}
